Environmental suitability throughout the late Quaternary explains population genetic diversity.

### 2023-08-08 manuscript_english.Rmd
fix R_0

In other words, $\mathbf{G}_o$ is the set of sites in the geography that present positive growth rates related to favorable conditions. If we take the set of places in environmental space where these values are greater than a threshold, we can define a volume in multidimensional space such that $R(\vec{e})$ is always positive and greater than this threshold, that is $\mathbf{N}_F(t) = \{\vec{e} | R_0(\vec{e}(t)) > k \}$.

@@

We start by considering this defined volume of the set of \(R_0\) as a
set of trajectories for each point from geographic space to
environmental space. Considering this rate fixed \(\mathbf{R}_0\) when
the population grows, that is,
\(\mathbf{N}_F(t) = \{\vec{e} | R(\vec{e}(t)) > 1 \}\) and therefore
any local population will have a positive growth rate.

>>>>

In other words, $\mathbf{G}_o$ is the set of sites in the geography that present positive growth rates related to favorable conditions. If we take the set of places in environmental space where these values are greater than a threshold, we can define a volume in multidimensional space such that $R(\vec{e})$ is always positive and greater than this threshold, that is $\mathbf{N}_F(t) = \{\vec{e} | R(\vec{e}(t)) > k \}$.

@@

We start by considering this defined volume of the set of \(R\) as a
set of trajectories for each point from geographic space to
environmental space. Considering this rate fixed \(\mathbf{R}\) when
the population grows, that is,
\(\mathbf{N}_F(t) = \{\vec{e} | R(\vec{e}(t)) > 1 \}\) and therefore
any local population will have a positive growth rate.
